### 2009-05-12 trunk/htdocs/surfactant.tex
Added surfactant figure
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@543 40876441-3496-0410-a613-a2fca35b2ae2

@@

@@

>>>>

In the following we retain $\xi_0 = 2.26$ but keep the same surface
tension cf. $\xi_0 = 1.13$, that is 0.047.

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Name & $\eta$ & $-A,B$ & $\kappa$ & $kT$ & $\epsilon$ & $\beta$ & $W$
     & $M$ & $M_\psi$\\
\hline
R022a & 1/6 & 0.03125 & 0.08 & 8.48231$\times 10^{-4}$ & 0.02 & 0.000 & 0.0 
      & 0.15 & 2.0 \\
R022d &  &  &  & & & 0.005 &  &  &  \\
\hline
R024a & 1/6 & 0.03125 & 0.08 & 4.24115$\times 10^{-4}$ & 0.02 & 0.00 & 0.0 
      & 0.15 & 2.0 \\
R024d & &  &  &  & & 0.005 &  &  &  \\
\hline
R026a & 0.025 & 0.003125 & 0.008 & 8.48231$\times 10^{-4}$ & 0.002 & 0.00
      & 0.0 & 2.0 & 2.0 \\
R026d & &  &  &  & & 0.0005 &  &  &  \\
\hline
R028a & 0.025 & 0.003125 & 0.008 & 4.24115$\times 10^{-4}$ & 0.002 & 0.00
      & 0.0 & 2.0 & 2.0 \\
R028d & &  &  &  & & 0.0005 &  &  &  \\
\hline
\end{tabular}
\caption{Equilibrium results for $\xi_0 = 2.26$, $\epsilon = \kappa/4$, and
$\sigma_0 = 0.047$.}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & $\bar{\psi}$ & $\psi_b$ & $\psi_{0\mathrm{eq}}$
     & $\sigma / \sigma_0$  & Comment \\
\hline
R022a &  $2.0\times 10^{-1}$ & $1.701\times 10^{-1}$ & $7.423\times10^{-1}$
      & 0.88 & ok\\
R022a &  $1.0\times 10^{-1}$ & $8.008\times 10^{-2}$ & $5.023\times10^{-1}$
      & 0.90  & ok\\
R022a &  $5.0\times 10^{-2}$ & $3.871\times 10^{-2}$ & $2.886\times10^{-1}$
      & 0.93 & ok\\
R022a &  $2.5\times 10^{-1}$ & $1.904\times 10^{-2}$ & $1.530\times10^{-1}$
      & 0.95 & ok\\
R022a &  $1.0\times 10^{-2}$ & $7.546\times 10^{-3}$ & $6.305\times10^{-2}$
      & 0.96 & ok \\
R022a &  $1.0\times 10^{-3}$ & $7.506\times 10^{-4}$ & $6.407\times10^{-3}$
      & 0.97 & ok\\
\hline
R024a &  $2.0\times 10^{-1}$ & $1.471\times 10^{-1}$ & $9.854\times10^{-1}$
      & 0.84 & ok\\
R024a &  $1.0\times 10^{-1}$ & $5.475\times 10^{-2}$ & $9.476\times10^{-1}$
      & 0.87 & ok\\
R024a &  $5.0\times 10^{-2}$ & $1.960\times 10^{-2}$ & $7.935\times10^{-1}$
      & 0.89 & ok\\
R024a &  $2.5\times 10^{-2}$ & $8.113\times 10^{-3}$ & $5.029\times10^{-1}$
      &  0.93 & ok\\
R024a &  $1.0\times 10^{-2}$ & $3.042\times 10^{-3}$ & $2.160\times10^{-1}$
      &  0.95 & ok\\
R024a &  $1.0\times 10^{-3}$ & $2.998\times 10^{-4}$ & $2.191\times10^{-2}$
      &  0.97 & ok\\
\hline
\end{tabular}
\label{table:xi226a}
\caption{Equilibrium results for $\xi_0 = 2.26$, $\epsilon = \kappa/4$
and $\sigma_0 = 0.047$ at 2 million time steps.}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & $\bar{\psi}$ & $\psi_b$ & $\psi_{0\mathrm{eq}}$
     & $\sigma / \sigma_0$  & Comment \\
\hline
R014a &  $2.0\times 10^{-1}$ & $1.551\times 10^{-1}$ & $7.718\times10^{-1}$
      & 0.90 & ok\\
R014a &  $1.0\times 10^{-1}$ & $7.072\times 10^{-2}$ & $5.193\times10^{-1}$
      & 0.92 & ok\\
R014a &  $5.0\times 10^{-2}$ & $3.384\times 10^{-2}$ & $2.889\times10^{-1}$
      & 0.94 & ok\\
R014a &  $2.5\times 10^{-2}$ & $1.661\times 10^{-2}$ & $1.494\times10^{-1}$
      & 0.96 & ok\\
R014a &  $1.0\times 10^{-2}$ & $6.578\times 10^{-3}$ & $6.060\times10^{-2}$
      & 0.98 & ok\\
R014a &  $1.0\times 10^{-3}$ & $6.542\times 10^{-4}$ & $6.098\times10^{-3}$
      & 0.99 & ok\\
\hline
R016a &  $2.0\times 10^{-1}$ & $1.231\times 10^{-1}$ & $9.897\times10^{-1}$
      & 0.88 & ok\\
R016a &  $1.0\times 10^{-1}$ & $3.779\times 10^{-2}$ & $9.652\times10^{-1}$
      & 0.89 & ok\\
R016a &  $5.0\times 10^{-2}$ & $1.101\times 10^{-2}$ & $7.988\times10^{-1}$
      & 0.92 & ok\\
R016a &  $2.5\times 10^{-2}$ & $4.87\times 10^{-3}$ & $4.57\times10^{-1}$
      & 0.95 & ok\\
R016a &  $1.0\times 10^{-2}$ & $1.973\times 10^{-3}$ & $1.813\times10^{-1}$
      & 0.97 & ok\\
R016a &  $1.0\times 10^{-3}$ & $2.016\times 10^{-4}$ & $1.77\times10^{-2}$
      & 0.99 & ok\\
\hline
\end{tabular}
\label{table:xi226}
\caption{Equilibrium results for $\xi_0 = 3.39$, $\epsilon = \kappa/4$.}
\end{center}
\end{table}

\begin{figure}
\begin{center}
\includegraphics{surfactant_fig1.eps}
\end{center}
\caption{Equilibrium results for one-dimensional simulations with
varying interfacial width $\xi_0$, all other physical parameters
being the same. In particular, $\epsilon = \kappa/4$ and $\beta = 0$.
The
left-hand column shows equilibrium isotherms with $1/K_L$ = 0.1 (red)
and $1/K_L$ = 0.01 (green). The circles are simulations and the lines
the theoretical prediction. The right-hand column shows the
corresponding reduction in surface tension at equilibrium
as a function of $\psi_{0,\mathrm{eq}}$. This reduction is scaled by
the bare interface surface tension $\sigma_0$. The exact result here
is based on a direct numerical integration of the excess free energy
across an equilibrium interfacial profile. The points are computed
by carrying out an analogous numerical integration of the simulated
profile at the given resolution. Note that the representation of
the surfactant porfile is particularly poor at $\xi_0 = 1.13$ as
there turn out to be an even number of lattice points where
$\psi >> \psi_b$ so that the peak value is missed.}
\end{figure}
